---
title: "The Israeli-Palestinian conflict: a multi-lingual sentiment analysis of wikipedia pages."
author:
  - name: "Raïsa Carmen, Wenting Jiang, Wendy Dewit (Group 19) "
abstract: >
  This research proposal proposes an application of sentiment analysis on wikipedia pages on the Israeli-Palestinian conflict. Using web crawling and web scraping, wikipedia pages on the Israeli-Palestinian conflict are gathered in different languages. Next, sentiment analysis is used to reveal the sentiment in each of the gathered documents. The research goal is to see whether some languages tend to have a more positive or negative sentiment towards the Israeli-Palestinian conflict, Israel, or Palestine.
keywords: [Israeli-Palestinian conflict, wikipedia, sentiment analysis]
# Date format: '%Y %B %d' for distill
date: "`r format(Sys.time(), '%Y %B %d')`"
url: https://github.com/raiisac/col_an_data_for_soc_sci.git
github-repo: GitHubID/Repository
lang: en-US
otherlangs: [fr-FR,it]
keywordlabel: Keywords
bibliography: references.bib
biblio-style: chicago
toc-depth: 3
fontsize: 10pt
urlcolor: blue
preamble: >
  \hyphenation{bio-di-ver-si-ty sap-lings}
always_allow_html: yes
csquotes: true
output:
  bookdown::pdf_book:
    template: latex/template.tex
    citation_package: natbib
    toc: no
    latex_engine: xelatex
    keep_tex: yes
    extra_dependencies: ["float", "stfloats"]
  rmdformats::downcute:
    use_bookdown: yes
    lightbox: yes
  bookdown::gitbook:
    config:
      download: "pdf"
      sharing:
        github: yes
  bookdown::html_document2:
    base_format: distill::distill_article
    toc: no
    toc_float: no
    code_folding: show
    highlight_downlit: yes
  bookdown::word_document2: default
---

```{r}
#| label: DoNotModify
#| include: false
### Utilities. Do not modify.
# Installation of packages if necessary
knitr::opts_chunk$set(fig.pos = "b!", out.extra = "")
InstallPackages <- function(Packages) {
  InstallPackage <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {
      install.packages(Package, repos = "https://cran.rstudio.com/")
    }
  }
  invisible(sapply(Packages, InstallPackage))
}

# Basic packages
InstallPackages(c("bookdown", "formatR", "kableExtra", "ragg"))

# kableExtra must be loaded 
if (knitr::opts_knit$get("rmarkdown.pandoc.to") == "docx") {
  # Word output (https://stackoverflow.com/questions/35144130/in-knitr-how-can-i-test-for-if-the-output-will-be-pdf-or-word)
  # Do not use autoformat (https://github.com/haozhu233/kableExtra/issues/308)
  options(kableExtra.auto_format = FALSE)
}
library("kableExtra")

# Chunk font size hook: allows size='small' or any valid Latex font size in chunk options
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r}
#| label: Options
#| include: false
### Customized options for this document
# Add necessary packages here
Packages <- c("tidyverse")
# Install them
InstallPackages(Packages)

# knitr options
knitr::opts_chunk$set(
  cache =   FALSE,    # Cache chunk results
  include = TRUE,     # Show/Hide chunks
  echo =    TRUE,     # Show/Hide code
  warning = FALSE,    # Show/Hide warnings
  message = FALSE,    # Show/Hide messages
  # Figure alignment and size
  fig.align = 'center', out.width = '80%',
  # Graphic devices (ragg_png is better than standard png)
  dev = c("ragg_png", "pdf"),
  # Code chunk format
  tidy = TRUE, tidy.opts = list(blank = FALSE, width.cutoff = 50),
  size = "scriptsize", knitr.graphics.auto_pdf = TRUE
  )
options(width = 50)

# ggplot style
library("tidyverse")
theme_set(theme_bw())
theme_update(
  panel.background = element_rect(fill = "transparent", colour = NA),
  plot.background = element_rect(fill = "transparent", colour = NA)
)
knitr::opts_chunk$set(dev.args = list(bg = "transparent"))

# Random seed
set.seed(973)

#other packages
library(rprojroot)
```

```{r, echo=FALSE, results='asis'}
#cat("\\onecolumn")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Introduction

The Israeli-Palestinian conflict has its origins in the late 19$^{th}$ and early 20$^{th}$ century when Jewish settlers arrived to Ottoman Palestine. In 1947, after the second world war, the United Nations (UN) partition plan officially split Palestine into and Arab state, Jewish state, and Jerusalem. Important aspects of conflict are the Israeli occupation of the West Bank and Gaza strip, Israeli settlements (see also Figure \@ref(fig:territory)), the division of Jerusalem, borders, security and water rights. Both parties have their supporters and this research aims to investigate whether a sentiment analysis of Wikipedia pages on the conflict in different languages can unveil underlying positive or negative feelings towards the conflict, Israel and Palestine.


Wikipedia pages are typically written by a community of interested and motivated volunteers. Wikipedia pages exist in many different languages and the content may differ quite substantially, depending on the language. They are typically not a literal translation from one language to the other but are written by speakers of the language with some knowledge on the topic at hand. We will focus on the languages spoken by Israeli (Hebrew and Yiddish), the Palestinians (Arab), some "Western" languages (English, Dutch, French, German, Italian, Spanish) and some Eastern languages (Chinese, Russian, Persian).

```{r territory, echo=FALSE, fig.cap= "Division of Palestinian and Israeli territory over the years (source: https://yalibnan.com/2014/06/27/eu-warns-business-israeli-settlements/)", out.width = "10cm"}
knitr::include_graphics(
  find_root_file("data", "fig", "vanishing-palestine.jpg",
                 criterion = has_file("col_an_data_for_soc_sci.Rproj")))
```


## Literature review

The Israeli-Palestinian conflict has been analysed using sentiment analysis before. In this section, we refer to some inspiring examples. 

The documents on which the sentiment analysis is applied differs over different research articles.  Twitter has likely been the most popular choice [@al2019multi; @imtiaz2022taking; @matalon2021using; @ramdhani2023sentiment; @abusheikh2023digital] but web scraping from Twitter's successor, X, has become very hard so we looked for alternatives.
@al2018bias identify patterns in the press orientation and further in the media bias towards either the Palestinian or Israeli side from press reports and articles.
Similarly, @alsubari2024online base their research on news channel streams to assess channel and user engagement. 

Other examples where opninions are compared in different languages are @abusheikh2023digital and @al2012automatic. The latter is of particular interest since they also base their research on wikipedia pages. 

# Methodology


We plan to follow the following steps:

1. Web scraping and web crawling: We plan to use the R package [\underline{rvest}](https://cran.r-project.org/web/packages/rvest/index.html) for this task, inspired by two tutorials in particular: [\underline{here}](https://ghanadatastuff.com/post/webscraping_wikipedia/) and [\underline{here}](https://github.com/tm4ss/tm4ss.github.io/blob/master/Tutorial_1_Web_scraping.Rmd). 
2. Sentiment analysis: Since we want to compare the sentiment of wikipedia pages in different languages, we need a tool that is able to perform sentiment analysis in different languages. The [\underline{Syuzhet}](https://cran.r-project.org/web/packages/syuzhet/vignettes/syuzhet-vignette.html) package currently supports many languages, among which all languages of interest as specified in the introduction.
3. A statistical analysis: It is yet unclear which statistical analysis will fit best to answer our main research questions pertaining to the difference in sentiment/opinion on the Israeli-Palestinian conflict, depending on the language of the documents. Finding clusters of languages with similar sentiments seems like a sensible route for now.



```{r, echo=FALSE, results='asis'}
#if you want the references in one column. This does appear on a new page then
cat("\\onecolumn")
```
